Influence of Time Integration Methodology on Double Detonation Type Ia Supernova Nucleosynthesis

### 2023-06-25 subch_tols/paper.tex
more updates

@@

We place a small temperature perturbation in the He layer using the
same form as in \citet{castro_simple_sdc}:
\begin{equation}
  T = T_0 \left \{ 1 + X(\isotm{He}{4}) f \left [1 + \tanh(2 - \sigma) \right ] \right \}
\end{equation}
where
\begin{equation}
  \sigma = \left [ x^2 + (y - R_0)^2 \right ]^{1/2} / \lambda
\end{equation}
and
\begin{equation}
  R_0 = R_\mathrm{pert} + R_\mathrm{base}
\end{equation}
where, $R_\mathrm{base}$ is the radius at which the helium layer
begins and $R_\mathrm{pert}$ is the distance above the base to put the
perturbation.  We choose $R_\mathrm{pert} = 100~\mathrm{km}$.  The
temperature is perturbed above the initial model value, denoted as
$T_0$ here.  The amplitude of the perturbation is $f = 3$ and the
scale of the perturbation is $\lambda = 12.5~\mathrm{km}$.  This is a
very small perturbation, but enough to seed the initial He detonation
in the envelope.  \MarginPar{give the peak temperature}

@@

@@

@@

>>>>

\author{Melissa Rasmussen}
\affiliation{Stony Brook? Utah?}

\author{Abigail Polin}
\affiliation{Caltech}

@@

We place a small temperature perturbation in the He layer using the
same form as in \citet{castro_simple_sdc}:
\begin{equation}
  T = T_0 \left \{ 1 + X(\isotm{He}{4}) f \left [1 + \tanh(2 - \sigma) \right ] \right \}
\end{equation}
where
\begin{equation}
  \sigma = \left [ x^2 + (y - R_0)^2 \right ]^{1/2} / \lambda
\end{equation}
and
\begin{equation}
  R_0 = R_\mathrm{pert} + R_\mathrm{base}
\end{equation}
where, $R_\mathrm{base}$ is the radius at which the helium layer
begins and $R_\mathrm{pert}$ is the distance above the base to put the
perturbation.  We choose $R_\mathrm{pert} = 100~\mathrm{km}$.  The
temperature is perturbed above the initial model value, denoted as
$T_0$ here.  The amplitude of the perturbation is $f = 3$ and the
scale of the perturbation is $\lambda = 12.5~\mathrm{km}$.  This is a
very small perturbation, with a peak temperature of about $1.1\times
10^9~\mathrm{K}$, but enough to seed the initial He detonation in the
envelope.

@@

Figure~\ref{fig:res_panel} shows a time sequence of the simplified-SDC
simulation with CFL = 0.2 and our standard tolerances
($\epsilon_\mathrm{abs} = \epsilon_\mathrm{rel} = 10^{-5}$ at 3
diferent spatial resolutions: 40 km, 20 km, and 10 km.  For the 40 km
run, we simply use one fewer levels of refinement compared to our base
simulation.  For the 10 km run, we add an additional level of
refinement that captures only the high temperature regions (including
the initial He layer) but with the very center always refined by
adding an additional refinement tagging criteria on densities $\rho >
7.5\times 10^7~\gcc$.  The first column of the figure shows the
initial grid structure---darker colors are higher levels of
refinement.  Each of the boxes shown is a multiple of 32 zones in each
dimension, with a maximum of 256 zones in any dimension.  This
refinement for the highest resolution run ensures that we capture the
convergence of the pressure wave at the center.

@@

As we see from the time-evolution, the three different resolutions all
behave largely the same.  The timescale for the He detonaiton to
propagate around the star and the timescale at which the second C
detonation ignite match well.  Figure~\ref{fig:res} shows the
\isot{Ni}{56} mass produced from the three different simulations.
Again, the agreement is quite strong.

@@

We note that these resolution results differ from the conclusions of
\citet{rivas:2022}.  There are a number of reasons why this might be
the case.  First the initial models differ \MarginPar{details}.
Second, we use a much larger reaction network here that better
captures the energetics.  This means that the He detonation moves
faster and the subsequent convergence of the pressure wave will be
more on-center, meaning that the ignition of the C detonation occurs
at a higher temperature.  Finally, we are using the simplified-SDC time-integration, which that work used Strang splitting \MarginPar{do they give details about e evolution?}
